An equivalence of compositional frameworks

### 2019-01-08 EquivCompFrameworks_20180911kc.tex
More notational changes

\begin{lem}
The double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is fibrant.
\end{lem}

\begin{proof}
Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $\mathbb{F} \textnormal{Cospan}(\mathrm{A})$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c^\prime$};
\node (C) at (2,0) {$c^\prime$};
\node (D) at (1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
and then obtain the following two 2-morphisms:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (3,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (G) at (4,0.5) {$c$};
\node (H) at (5,0.5) {$c$};
\node (I) at (6,0.5) {$c$};
\node (G') at (4,-0.5) {$c$};
\node (H') at (5,-0.5) {$c^\prime$};
\node (I') at (6,-0.5) {$c^\prime$};
\node (J) at (7,0.5) {$!_{c} \in F(c)$};
\node (K) at (7,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (L) at (1,-1) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
\node (M) at (5,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$1$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$f$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
which satisfy the equations:
\[
\begin{tikzpicture}[scale=1.5]
\node (N) at (0,1.5) {$c$};
\node (O) at (1,1.5) {$c$};
\node (P) at (2,1.5) {$c$};
\node (Q) at (-1,1.5) {$!_c \in F(c)$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (-1,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (-1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (G) at (4,1) {$c$};
\node (H) at (5,1) {$c$};
\node (I) at (6,1) {$c$};
\node (G') at (4,0) {$c^\prime$};
\node (H') at (5,0) {$c^\prime$};
\node (I') at (6,0) {$c^\prime$};
\node (J) at (7,1) {$!_{c} \in F(c)$};
\node (K) at (7,0) {$!_{c^\prime} \in F(c^\prime)$};
\node (Q) at (1,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
\node (M) at (5,-0.5) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\node (R) at (3,0.5) {$=$};
\path[->,font=\scriptsize,>=angle 90]
(N) edge node[above]{$1$} (O)
(P) edge node[above]{$1$} (O)
(N) edge node[left]{$1$} (A)
(O) edge node[left]{$f$} (B)
(P) edge node[left]{$f$} (C)
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$f$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$1$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$c$};
\node (H) at (-1,-0.5)  {$c^\prime$};
\node (I) at (-2,0.5) {$c$};
\node (J) at (-2,-0.5) {$c$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (1,1) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (1,-1) {$!_{c^\prime} \in F(c^\prime)$};

@@

\begin{thm}
There exists a symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ which has:
\begin{enumerate}
\item{objects as those of $\mathrm{A}$,}
\item{morphisms as pairs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\mathrm{A}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-0.5) {$c^\prime$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o^\prime$} (E);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{thm}

\begin{proof}
This follows immediately by Shulman's Theorem \ref{Shul} above.
\end{proof}

This symmetric monoidal bicategory is a superior version of the symmetric monoidal bicategory constructed earlier by the second author \cite{Cour}. The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction. Given a symmetric lax monoidal functor $F \colon \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
\begin{enumerate}
\item{objects as those of $\mathrm{A}$ and}
\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
\end{enumerate}
The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
\begin{enumerate}
\item{objects as those of $\mathrm{A}$,}
\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
\item{2-morphisms as pairs of commuting diagrams:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0.5) {$c$};
\node (B') at (1,-0.5) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (3,0) {$1$};
\node (E) at (4,0.5) {$F(c)$};
\node (E') at (4,-0.5) {$F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (B')
(C) edge node[below]{$o^\prime$} (B')
(B) edge node [left] {$f$} (B')
(D) edge node [above] {$d$} (E)
(D) edge node [below] {$d^\prime$} (E')
(E) edge node [right] {$F(f)$} (E');
\end{tikzpicture}
\]
}
\end{enumerate}
This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e$} (B);
\end{tikzpicture}
\]
and
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$v_1$};
\node (B) at (1,0) {$v_2.$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$e^\prime$} (B);
\end{tikzpicture}
\]
resided in distinct isomorphism classes. In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above. This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \colon F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.

@@

We can the decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category similar to the one obtained using Fong's result:

\begin{cor}
Given a symmetric lax monoidal pseudofunctor $F \colon \mathrm{A} \to \mathbf{Cat}$ where $\mathrm{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $D(H(\mathbb{F}\textnormal{Cospan}(\mathrm{A})))$ which has:
\begin{enumerate}
\item{objects as those of $\mathrm{A}$ and}
\item{morphisms as isomorphism classes of $F$-decorated cospans of $\mathrm{A}$, where an $F$-decorated cospan is given by a pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
Given another $F$-decorated cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B);
\end{tikzpicture}
\]
these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon c \to c^\prime$ such that following diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B') at (1,0.5) {$c$};
\node (B) at (1,-0.5) {$c^\prime$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B)
(A) edge node[above]{$i$} (B')
(C) edge node[above]{$o$} (B')
(B') edge node[left]{$f$} (B);
\end{tikzpicture}
\]
and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{cor}
In this symmetric monoidal category, isomorphism classes are as they should morally be, and the instance of two graphs having different edge sets does not prevent them from being in the same isomorphism class due to the isomorphism $\iota$.

@@

Let $F \colon \mathrm{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor. Then by Theorem \ref{main1} of the previous section, we get a symmetric monoidal double category $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$. This symmetric monoidal double category has:

@@

\item{objects as those of $\mathrm{A}$,}
\item{vertical 1-morphisms as morphisms of $\mathrm{A}$,}

@@

\item{2-morphisms as maps of cospans in $\mathrm{A}$

@@

Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathrm{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$. Then a map from $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ to $\mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ will be a double functor $\mathbb{H} \colon \mathbb{F}\textnormal{Cospan}(\mathrm{A}) \to \mathbb{F^\prime}\textnormal{Cospan}(\mathrm{A^\prime})$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathrm{A} \to \mathrm{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:

@@

where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a terminal category preserving 2-functor such that the following diagram commutes:
\node (A) at (0,0) {$\mathrm{A}$};

@@

\node (C) at (0,-1) {$\mathrm{A^\prime}$};

@@

Applying the terminal category preserving 2-functor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
\node (A) at (0,-0.5) {$E(1) \cong 1$};

@@

\node (A) at (0,-0.5) {$E(1) \cong 1$};

@@

which is the same as a morphism $E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$ in $F^\prime(H(c^\prime))$. To check that the above recipe is functorial, given two vertically composable 2-morphisms in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:

@@

Given two composable horizontal 1-cells $M$ and $N$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$:

@@

\node (B) at (1.5,0) {$H(c_1+_b c_2)$};
\node (C) at (3,0) {$H(a_2)$};
\node (D) at (1.5,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};

@@

\node (B) at (2,0) {$H(c_1)+_{H(b)} H(c_2)$};
\node (D) at (2,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};

@@

\node (F) at (7,-0.5) {$d \in F^\prime(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d^\prime) \to d.$};

@@

where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ which comes from the functor $H \colon \mathrm{A} \to \mathrm{A^\prime}$ preserving finite colimits. The above diagram commutes by a similar argument as to the one used in Theorem \ref{main2}. Similarly we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:

@@

where the morphism of decorations is the identity $!_{H(c)} = E(!_c)$ as $EF=F^\prime H$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:

@@

(A') edge node [right]{$1 \odot \mathbb{H}_{N \odot P}$} (B');

@@

their tensor product $M_1 \otimes M_2$ in $\mathbb{F}\textnormal{Cospan}(\mathrm{A})$ is given by:

@@

\node (D) at (1.5,-0.5) {$d_1+d_2 \in F(c_1)$};

@@

(B') edge node [right] {$\mathbb{H}_{M_1,M_2 \otimes M_3}$} (C')

@@

(F) edge node[above]{$1$} (G)

>>>>

\begin{lem}
The double category $F\mathbb{C}\textnormal{sp}$ is fibrant.
\end{lem}

\begin{proof}
Let $f \colon c \to c^\prime$ be a vertical 1-morphism in $F\mathbb{C}\textnormal{sp}$. We can lift $f$ to the companion horizontal 1-cell $\hat{f}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c$};
\node (B) at (1,0) {$c^\prime$};
\node (C) at (2,0) {$c^\prime$};
\node (D) at (1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
and then obtain the following two 2-morphisms:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (3,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (3,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (G) at (4,0.5) {$c$};
\node (H) at (5,0.5) {$c$};
\node (I) at (6,0.5) {$c$};
\node (G') at (4,-0.5) {$c$};
\node (H') at (5,-0.5) {$c^\prime$};
\node (I') at (6,-0.5) {$c^\prime$};
\node (J) at (7,0.5) {$!_{c} \in F(c)$};
\node (K) at (7,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (L) at (1,-1) {$\iota_{1_{c^\prime}} = 1_{!_{c^\prime}}$};
\node (M) at (5,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$1$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$f$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
which satisfy the equations:
\[
\begin{tikzpicture}[scale=1.5]
\node (N) at (0,1.5) {$c$};
\node (O) at (1,1.5) {$c$};
\node (P) at (2,1.5) {$c$};
\node (Q) at (-1,1.5) {$!_c \in F(c)$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (-1,0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (-1,-0.5) {$!_{c^\prime} \in F(c^\prime)$};
\node (G) at (4,1) {$c$};
\node (H) at (5,1) {$c$};
\node (I) at (6,1) {$c$};
\node (G') at (4,0) {$c^\prime$};
\node (H') at (5,0) {$c^\prime$};
\node (I') at (6,0) {$c^\prime$};
\node (J) at (7,1) {$!_{c} \in F(c)$};
\node (K) at (7,0) {$!_{c^\prime} \in F(c^\prime)$};
\node (Q) at (1,-1) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\node (L) at (1,-1.5) {$\iota_{c^\prime} = 1_{!_{c^\prime}}$};
\node (M) at (5,-0.5) {$\iota_f \colon F(f)(!_c) \to !_{c^\prime}$};
\node (R) at (3,0.5) {$=$};
\path[->,font=\scriptsize,>=angle 90]
(N) edge node[above]{$1$} (O)
(P) edge node[above]{$1$} (O)
(N) edge node[left]{$1$} (A)
(O) edge node[left]{$f$} (B)
(P) edge node[left]{$f$} (C)
(A) edge node[above]{$f$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$f$} (A')
(C) edge node[left]{$1$} (C')
(A') edge node[above] {$1$} (D)
(C') edge node[above] {$1$} (D)
(B) edge node [left] {$1$} (D)
(G) edge node [above] {$1$} (H)
(G) edge node [left] {$f$} (G')
(H) edge node [left] {$f$} (H')
(G') edge node [above] {$1$} (H')
(I) edge node [above] {$1$} (H)
(I) edge node [left] {$f$} (I')
(I') edge node [above] {$1$} (H');
\end{tikzpicture}
\]
\[
\begin{tikzpicture}[scale=1.5]
\node (G) at (-1,0.5) {$c$};
\node (H) at (-1,-0.5)  {$c^\prime$};
\node (I) at (-2,0.5) {$c$};
\node (J) at (-2,-0.5) {$c$};
\node (A) at (0,0.5) {$c$};
\node (A') at (0,-0.5) {$c^\prime$};
\node (B) at (1,0.5) {$c^\prime$};
\node (C) at (2,0.5) {$c^\prime$};
\node (C') at (2,-0.5) {$c^\prime$};
\node (D) at (1,-0.5) {$c^\prime$};
\node (E) at (1,1) {$!_{c^\prime} \in F(c^\prime)$};
\node (F) at (1,-1) {$!_{c^\prime} \in F(c^\prime)$};

@@

\begin{cor}
Let $(\mathsf{C},+,0)$ be a category with finite colimts and $F \colon \mathsf{C} \to \mathbf{Cat}$ a symmetric lax monoidal pseudofunctor. Then there exists a symmetric monoidal bicategory $F \mathbf{Csp} \coloneqq H(F\mathbb{C}\textnormal{sp})$ which has:
\begin{enumerate}
\item{objects as those of $\mathsf{A}$,}
\item{morphisms as $F$-decorated cospans:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
and}
\item{2-morphisms as maps of cospans in $\mathsf{A}$ of the form:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0.5) {$c$};
\node (C) at (2,0) {$b$};
\node (E) at (1,-0.5) {$c^\prime$};
\node (D) at (3,0.5) {$d \in F(c)$};
\node (F) at (3,-0.5) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B)
(A) edge node[below]{$i^\prime$} (E)
(B) edge node[left]{$h$} (E)
(C) edge node[below]{$o^\prime$} (E);
\end{tikzpicture}
\]
together with a morphism $\iota \colon F(h)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{cor}

\begin{proof}
This follows immediately by Shulman's Theorem \ref{Shul} above applied to the fibrant symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$.
\end{proof}

This symmetric monoidal bicategory $F\mathbf{Csp}$ is a superior version of the symmetric monoidal bicategory $F$Cospan$(\mathsf{A})$ constructed earlier by the second author \cite{Cour} in that there is greater flexibility in what 2-morphisms are allowed.

%The previous bicategory constructed by the second author suffered even more so from the issue discussed in the introduction. Given a symmetric lax monoidal functor $F \colon \mathrm{A} \to \mathrm{Set}$, a result of Fong \cite{Fong} yields a symmetric monoidal category $F \textnormal{Cospan}(\mathrm{A})$ which has:
%\begin{enumerate}
%\item{objects as those of $\mathrm{A}$ and}
%\item{morphisms as isomorphism classes of decorated cospans in $\mathrm{A}$.}
%\end{enumerate}
%The second author then using a result of Shulman \cite{Shul} extended this to a bicategory also called $F \textnormal{Cospan}(\mathrm{A})$ which has:
%\begin{enumerate}
%\item{objects as those of $\mathrm{A}$,}
%\item{morphisms as now just decorated cospans in $\mathrm{A}$, and}
%\item{2-morphisms as pairs of commuting diagrams:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$a$};
%\node (B) at (1,0.5) {$c$};
%\node (B') at (1,-0.5) {$c^\prime$};
%\node (C) at (2,0) {$b$};
%\node (D) at (3,0) {$1$};
%\node (E) at (4,0.5) {$F(c)$};
%\node (E') at (4,-0.5) {$F(c^\prime)$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$i$} (B)
%(C) edge node[above]{$o$} (B)
%(A) edge node[below]{$i^\prime$} (B')
%(C) edge node[below]{$o^\prime$} (B')
%(B) edge node [left] {$f$} (B')
%(D) edge node [above] {$d$} (E)
%(D) edge node [below] {$d^\prime$} (E')
%(E) edge node [right] {$F(f)$} (E');
%\end{tikzpicture}
%\]
%}
%\end{enumerate}
%This was discussed in the introduction and it was mentioned how in the symmetric monoidal category version of $F \textnormal{Cospan}(\mathrm{A})$, that the two single-edged graphs:
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$v_1$};
%\node (B) at (1,0) {$v_2$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$e$} (B);
%\end{tikzpicture}
%\]
%and
%\[
%\begin{tikzpicture}[scale=1.5]
%\node (A) at (0,0) {$v_1$};
%\node (B) at (1,0) {$v_2.$};
%\path[->,font=\scriptsize,>=angle 90]
%(A) edge node[above]{$e^\prime$} (B);
%\end{tikzpicture}
%\]
%resided in distinct isomorphism classes. In the bicategorical version of $F \textnormal{Cospan}(\mathrm{A})$ where we are no longer considering decorated cospans up to isomorphism class, there is no 2-morphism between these two graphs due to the strict commutativity of the triangle to the right above. This problem does not occur in the symmetric monoidal bicategory $H(\mathbb{F}\textnormal{Cospan}(\mathrm{A}))$ and there is in fact a 2-(iso)morphism between these two graphs given by the map $\iota \colon F(f)(d) \to d^\prime$ which maps the edge $e$ to the edge $e^\prime$, where $f$ is the underlying map of vertices.

@@

We can then decategorify this symmetric monoidal bicategory to obtain a symmetric monoidal category similar to the one obtained using Fong's result, but with larger isomorphism classes:

\begin{cor}
Given a symmetric lax monoidal pseudofunctor $F \colon \mathsf{A} \to \mathbf{Cat}$ where $\mathsf{A}$ is a category with finite colimits and whose monoidal structure is given by binary coproducts, there exists a symmetric monoidal category $F\textnormal{Csp} \coloneqq D(F\mathbf{Csp})$ which has:
\begin{enumerate}
\item{objects as those of $\mathsf{A}$ and}
\item{morphisms as isomorphism classes of $F$-decorated cospans of $\mathsf{A}$, where an $F$-decorated cospan is given by a pair:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$i$} (B)
(C) edge node[above]{$o$} (B);
\end{tikzpicture}
\]
Given another $F$-decorated cospan:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B) at (1,0) {$c^\prime$};
\node (C) at (2,0) {$b$};
\node (D) at (4,0) {$d^\prime \in F(c^\prime)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B);
\end{tikzpicture}
\]
these two $F$-decorated cospans are in the same isomorphism class if there exists an isomorphism $f \colon c \to c^\prime$ such that following diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$a$};
\node (B') at (1,0.5) {$c$};
\node (B) at (1,-0.5) {$c^\prime$};
\node (C) at (2,0) {$b$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[below]{$i^\prime$} (B)
(C) edge node[below]{$o^\prime$} (B)
(A) edge node[above]{$i$} (B')
(C) edge node[above]{$o$} (B')
(B') edge node[left]{$f$} (B);
\end{tikzpicture}
\]
and there exists an isomorphism $\iota \colon F(f)(d) \to d^\prime$ in $F(c^\prime)$.}
\end{enumerate}
\end{cor}
In this symmetric monoidal category, isomorphism classes are as they should morally be, and the instance of two graphs having different edge sets does not prevent them from being in the same isomorphism class due to the isomorphism $\iota$.

@@

Let $F \colon \mathsf{A} \to \mathbf{Cat}$ be a symmetric lax monoidal pseudofunctor. Then by Theorem \ref{DC} of the previous section, we get a symmetric monoidal double category $F\mathbb{C}\textnormal{sp}$. This symmetric monoidal double category has:

@@

@@

\item{2-morphisms as maps of cospans in $\mathsf{A}$

@@

Given another symmetric lax monoidal pseudofunctor $F^\prime \colon \mathsf{A^\prime} \to \mathbf{Cat}$, we can obtain another symmetric monoidal double category $F^\prime \mathbb{C}\textnormal{sp}$. Then a map from $F\mathbb{C}\textnormal{sp}$ to $F^\prime \mathbb{C}\textnormal{sp}$ will be a double functor $\mathbb{H} \colon F\mathbb{C}\textnormal{sp} \to F' \mathbb{C}\textnormal{sp}$ whose object component is given by a finite colimit preserving functor $\mathbb{H}_0 = H \colon \mathsf{A} \to \mathsf{A^\prime}$ and whose arrow component is given by a functor $\mathbb{H}_1$ defined on horizontal 1-cells by:

@@

where $E \colon \mathbf{Cat} \to \mathbf{Cat}$ is a symmetric lax monoidal pseudofuctor such that the following diagram commutes:
\node (A) at (0,0) {$\mathsf{A}$};

@@

\node (C) at (0,-1) {$\mathsf{A^\prime}$};

@@

Applying the pseudofunctor $E \colon \mathbf{Cat} \to \mathbf{Cat}$ to this diagram yields:
\node (A) at (0,-0.5) {$1 \xrightarrow{\sim} E(1)$};

@@

\node (A) at (0,-0.5) {$1 \xrightarrow{\sim} E(1)$};

@@

which is the same as a morphism $E(\iota) \colon F^\prime(H(h))(E(d)) \to E(d^\prime)$ in $F^\prime(H(c^\prime))$. To check that the above recipe is functorial, given two vertically composable 2-morphisms in $F\mathbb{C}\textnormal{sp}$:

@@

Given two composable horizontal 1-cells $M$ and $N$ in $F\mathbb{C}\textnormal{sp}$:

@@

\node (B) at (2,0) {$H(c_1+_b c_2)$};
\node (D) at (2,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};

@@

\node (B) at (2.25,0) {$H(c_1)+_{H(b)} H(c_2)$};
\node (C) at (4.5,0) {$H(a_2)$};
\node (D) at (2.25,-0.5) {$d^\prime \in F^\prime(H(c_1) +_{H(b)} H(c_2))$};

@@

\node (F) at (7,-0.5) {$E(d) \in F^\prime(H(c_1 +_b c_2))$};
\node (G) at (2.5,-1) {$\iota_{\kappa^{-1}} \colon F^\prime(\kappa^{-1})(d^\prime) \to E(d).$};

@@

where $\kappa$ is the isomorphism $$\kappa \colon H(c_1 +_b c_2) \xrightarrow{\sim} H(c_1) +_{H(b)} H(c_2)$$ comes from the finite colimit preserving functor $H \colon \mathsf{A} \to \mathsf{A^\prime}$. The above diagram commutes by a similar argument to the one used in Theorem \ref{Equiv}. Similarly we have a unit comparison constraint $$\mathbb{H}_U \colon U_{\mathbb{H}(c)} \to \mathbb{H}(U_c)$$ given by the globular 2-isomorphism:

@@

where the morphism of decorations is the morphism $\iota \colon !_{H(c)} \to E(!_c)$ in $F'(H(c))$. These comparison constrains satisfy the coherence axioms of a monoidal category, namely:

@@

(A') edge node [right]{$1 \odot \mathbb{H}_{N,P}$} (B');

@@

their tensor product $M_1 \otimes M_2$ in $F\mathbb{C}\textnormal{sp}$ is given by:

@@

\node (D) at (1.5,-0.5) {$d_1+d_2 \in F(c_1+c_2)$};

@@

(B') edge node [right] {$\mu_{M_1,M_2 \otimes M_3}$} (C')

@@

%(F) edge node[above]{$1$} (G)
%(H) edge node[above]{$1$} (G);
